---
title: "DataMining_Process"
output:
  html_document: default
  pdf_document: default
---
        
                    STEPS FOR DATA MINING PROCESS...........
        
    1) load the dataset
    2) clean the data or pre-process the data
    3) understand data use visual effact that is- (ggplot2::)
    4) split your data into test and train
    5) create model on train & predict on test.
    6) Than see the model accuracy ........
____________________________________________________________________________
                        AT THE END OF STEP CHECK YOUR MODEL ACCURECY.......
____________________________________________________________________________
                    IF YOU SEE THIS SIGN(#) IT MEANS IT'S OPTIONAL PART.....


STEP-1 :  Load the dataset


```{r}
library(psych)#(Optional)
Data = read.csv("C:/Users/Dell/Desktop/data.csv")
describe(Data)#(Optional)
#You can also use summary function for Summarization purpose.......... 
```


STEP-2 :  Clean the data or pre-process the data


```{r}
cal = mean(Data$Calories,na.rm = T)
Data$Calories = ifelse(is.na(Data$Calories),cal,Data$Calories)
```

STEP-3 : To understand data we use graph
```{r}
library(ggplot2)
ggplot(Data) + geom_point(aes(x = Maxpulse,y = Pulse),color = "darkblue") + geom_smooth(aes(x = Maxpulse ,y = Pulse))
```

STEP-4 : Split your data into test and train

```{r}
Data$no = c(1:dim(Data)[1])#(We have to add new column for split data into test & train)

#(As below we split data into test & train)
Train = subset(Data,Data$no <= 135)
Test = subset(Data,Data$no > 135)

#(After split data we have to delete column which we added)
Data = Data[-5]
Train = Train[-5]
Test = Test[-5]
```


STEP-5 : Create model on train & predict on test
```{r}
lm_model = lm(Duration ~.,data = Train)
predect = predict(lm_model ,newdata = Test)

```

```{r}
compare_result = cbind(actual = Test$Duration , predect = predect)#(we created another dataframe and we added ac-tual test column and predicted test column for check the error..or model)
compare_result = as.data.frame(compare_result)
compare_result$error = compare_result$actual - compare_result$predec #(Now in same dataframe we added new column which is actual test data -(minus) predicted test data)
rmse = sqrt(mean(compare_result$error^2)) #(Now we do Square Root mean on error column.)
```

```{r}
summary(lm_model)#(Now.. AS BELOW YOU CAN SEE OUR MODEL IS 0.8911% CORRECT....)
```

